---
title: "Coursera Developing Data Products Course Project"
author: "Catherine Okuboyejo"
date: "27 January 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

##A Shiny Application

- The shiny application pitched in this presentation is here [link]

- The Shiny app source code is here [link]

##What does the app do?
- Allows you to visualise the areas of US states in square miles using the US State Facts and Figures dataset. 

- You can use sliders to select an area range to display and checkboxes to show different regions

- The output is an interactive map of the US showing the states that satisfy the selected criteria.

##Under the hood
```{r}
states <- data.frame(state.name, state.area, state.region,
                     hover=paste0(state.name, ": ", 
                                               state.area, " square miles"))
states$hover <- as.character(states$hover)

```

- A data frame called `states` was created using the vectors from the US Facts and Figures Dataset.

- A fourth column (`hover`) was added for the interactivity of the map.

```{r, echo=TRUE}
head(states)
```



##Output
- The slider values and checkbox values are used to filter the dataset using the `state.name` and `state.region` columns before creating the map.

- The output is a googlevis interactive map.

- The states turn green when they satisfy the selected criteria (slider and checkboxes)

- When each green state is hovered over, the name and area of the state is displayed.
